% Abstract

%\renewcommand{\abstractname}{Abstract} % Uncomment to change the name of the abstract

\pdfbookmark[1]{Abstract}{Abstract} % Bookmark name visible in a PDF viewer

\begingroup


\chapter*{Abstract}


\\

Nowadays technology tries to adapt to the interest of every user, software developers try to satisfy their clients creating new apps for each kind of user, furthermore this users can have different devices with different Operating systems, this leads application developers to find different solutions to satisfy their own clients needs without decreasing its own revenue by using only the necessary services that an application needs.
\\

An approach to provide those services to be efficient for users and providers is by utilizing Cloud computing which is an internet based computing for providing storage, compute and networking services remotely stored in a data center.
\\

This project presents how docker containers and a virtualization environment can provide those services and how OpenvSwitch gives an approach to manage the communication between them on the level of the underlay network which is the one running inside of another network in this case the network between containers that are inside of the virtual machines.
\\

This project also presents a theoretical insight on how to manage the overlay infrastructure in the case of inter-connectivity between different hosts or virtual machines.
\\

Finally the project project presents the terminology and use cases for docker containers in container migration.
\\

This project seeks to answer the next questions:\\

- Which types of network configuration there are among docker containers and docker-machine (virtual-machine)?

- What are the features needed while configuring an infrastructure with docker?.

- How does docker swarm works and why is it related to the overlay network?

- Why OpenvSwitch is applied instead of Linux Bridge?

- How to add the OpenStack configuration to the project?

- How to migrate a container from one server to another without losing its state?\\

This document also presents all the functions that docker provides and the usage of docker containers, namespaces, docker virtual machines, swarm nodes, overlay and underlay network, checkpoints and container migration.

 



\endgroup			

\vfill